---
title: "Text Analysis I - Exercise I"
date: July 11, 2024
format: 
  html:
    embed-resources: true
    number-sections: true
editor: visual
execute: 
  eval: false
  echo: true
  output: false
  warning: false
  error: false
---

# Preparation

Packages you will (probably) need:

```{r}
library(dplyr)
library(quanteda)
library(quanteda.sentiment)
library(seededlda)
library(quanteda.textmodels)
```

Use the script from exercise 1 to get all the necessary objects for the analysis

# Perform a sentiment analysis

Get a dictionary from the quanteda.sentiment package and calculate the polarity (or valence) sentiment for each document:

```{r}

```

# Perform a topic models analysis

Use the quantda.texmodel function for a explorativ approach or define some seeds if you expect some topics with seeded lda:

```{r}

```

# **Bonus**: Train your own naive bayes classifier for sentiment

Get a training set from the labeled data and define classes:

```{r}

```

Train the model with the training data and classes:

```{r}

```

Get (unlabelled) test data:

```{r}

```

Predict class for test data with trained model:

```{r}

```

Create a simple confusion matrix to check prediction accuracy:

```{r}

```
