---
title: "Cleaning"
date: July 10, 2024
format:  html
editor: visual
execute: 
  eval: false
  echo: true
  output: false
  warning: false
  error: false
---

## Task: Clean and check the provided CNN data according to the instructions below.

This data set includes a random set of 500 CNN articles from 2020 and 2021 identified with the search term "black lives matter" and scraped in 2023.

```{r}
cnn_data <- readRDS("exercises/Ilaria_new/day3/data/CNN_cleaning.Rds")
```

### Cleaning the data

1.  **authors**: Separate the authors into different columns
2.  **timestamp**: Create the following three variables, and discard the rest of the information.
    a.  one that includes the information whether the article was updated or published on this date.
    b.  one that holds the weekday.
    c.  one that holds the date (in date format!).
3.  **title** and **body**:
    a.  remove non-language (e.g., html-notation and excessive white spaces)
    b.  remove all capitalization

**Bonus cleaning task** (difficult!): Change author names to be surname first, i.e., Lisa Smith becomes Smith, Lisa.

### Checking the data

Performing simple counting tasks, such as determining article length, word frequency, and the number of articles over time, helps identify errors in data collection or cleaning. For instance, a misspelled search term might result in fewer articles found, or unusually short articles could indicate data issues.

1.  Count the length of articles, calculate the mean length of articles, and count the overall number of characters in this corpus
2.  Count how often "Black Lives Matter" or "BLM" are mentioned in individual articles and titles and think about the implications of the results
3.  Count the number of articles by month

Bonus task: Count how many articles that include "Black Lives Matter" or "BLM" also include the words related to riots

### Packages you will probably need

```{r}
library(tidyverse) # stringr is part of the tidyverse
library(lubridate)
```

## Complete the tasks below here

(you can add additional code chunks with ctrl+alt+i / or ⌥⌃i)

### Cleaning the data

#### 1. authors: Separate the authors into different columns

```{r}
df_ila <- cnn_data %>%
  separate(authors, into = c("Author1", "Author2", "Author3", "Author4", "Author5"), sep = ";|with", fill = "right")

```

#### 2. timestamp: Create the following three variables, and discard the rest of the information.

a.  one that includes the information whether the article was updated or published on this date.
b.  one that holds the weekday.
c.  one that holds the date (in date format!).

```{r}
# a. status
df_ila <- df_ila %>%
  mutate(status = str_extract(timestamp, "(Updated|Published)"))

# b. weekday
df_ila <- df_ila %>%
  mutate(weekday = str_extract(timestamp, "(Mon|Tue|Wed|Thu|Fri|Sat|Sun)"))

# c. date
df_ila <- df_ila %>%
  mutate(date = mdy(str_extract(timestamp, "[A-Za-z]+ [0-9]{1,2}, [0-9]{4}")))

```

#### 3. title and body:

a.  remove all capitalization
b.  remove non-language (e.g., html-notation and excessive white spaces)

```{r}
# remove capitalization
df_ila <- df_ila %>% mutate(body = str_to_lower(body, locale = "en"))

# remove non language
df_ila <- df_ila %>% mutate(body=str_replace_all(body, "\\s+"," "))

```

### Checking the data

#### 1. Count the length of articles, calculate the mean length of articles, and count the overall number of characters in this corpus

```{r}
# count the length of articles
df_ila <- df_ila %>%
  mutate(char_count = nchar(body))

# calculate mean length
mean(df_ila$char_count)

# count overall characters in the corpus
sum(df_ila$char_count)

```

#### 2. Count how often "Black Lives Matter" or "BLM" are mentioned in individual articles and titles and think about the implications of the results

```{r}

# how often 
df_ila <- df_ila %>%
  mutate(BLM_count_art=str_count(body, regex("\\b(Black Lives Matter|BLM)\\b", ignore_case = TRUE)), BLM_count_tit=str_count(title, regex("\\b(Black Lives Matter|BLM)\\b", ignore_case = TRUE)))


```

#### 3. Count the number of articles by month

```{r}
# create year and month col
df_ila <- df_ila %>%
  mutate(year = year(date), month = month(date))
# group by
count_art <- df_ila %>% group_by(month, year) %>% count()
```
