---
title: "Text Analysis I - Exercise I"
date: July 11, 2024
format: 
  html:
    embed-resources: true
    number-sections: true
editor: visual
execute: 
  eval: false
  echo: true
  output: false
  warning: false
  error: false
---

# Preparation

Packages you will (probably) need:

```{r}
install.packages("remotes")
remotes::install_github("quanteda/quanteda.sentiment")
library(dplyr)
library(quanteda)
library(quanteda.sentiment)
library(seededlda)
library(quanteda.textmodels)
```

Use the script from exercise 1 to get all the necessary objects for the analysis

# Perform a sentiment analysis

Get a dictionary from the quanteda.sentiment package and calculate the polarity (or valence) sentiment for each document:

```{r}

head(data_dictionary_HuLiu)
head(data_dictionary_LSD2015)

dict_pol <- data_dictionary_HuLiu

dfm_lookup(dfm_pp, dict_pol)

textstat_polarity(dfm_pp, dict_pol)

textstat_valence(dfm_pp, data_dictionary_AFINN)
```

# Perform a topic models analysis

Use the quantda.texmodel function for a explorativ approach or define some seeds if you expect some topics with seeded lda:

```{r}
library(quanteda.textmodels)
library(seededlda)

tmod_lda <- textmodel_lda(dfm_pp, k = 5)

terms(tmod_lda, 10)

topics(tmod_lda)|>
  head(10)
```

# **Bonus**: Train your own naive bayes classifier for sentiment

Get a training set from the labeled data and define classes:

```{r}
library(quanteda.textmodels)

#get a training set dfmat_train
set.seed(123)

# Specify the number of documents you want in your smaller training set
num_docs <- 200  # Adjust this number as needed

# Sample a subset of documents from the DFM
dfm_train <- dfm_sample(dfm_pp, size = num_docs)

# Print the smaller DFM to verify
print(dfm_train)

#define classes
tmod_nb <- textmodel_nb(dfm_train, class)

summary(tmod_nb)

predicted_class <- predict(tmod_nb, dfm_train)

tab_class <- table(class, predicted_class)
caret::confusionMatrix(tab_class, mode = "everything")

```

Train the model with the training data and classes:

```{r}

```

Get (unlabelled) test data:

```{r}

```

Predict class for test data with trained model:

```{r}

```

Create a simple confusion matrix to check prediction accuracy:

```{r}

```
