---
title: "String Operations"
date: July 10, 2024
format:  html
editor: visual
execute: 
  eval: false
  echo: true
  output: false
  warning: false
  error: false
---

```{r}
library(tidyverse) #stringr is part of the tidyverse
```

```{r}
text <- "   I hope you will have a great time during the 9 days of SICSS-Berlin.  Orange  \nIf you have any suggestions for impovemend, feel free to tell us in person or via sicss.2023@wzb.eu.    Orange "
```

### Use `stringr` package, to solve the following tasks.

**Check out the stringr_cheatsheet.pdf in the day3_data_cleanup folder!**

#### Is there a line break present? Show using a function

```{r}

linebreak <- function(x) {
  website <- read_html()
gsub("[\r\n]", "", text)
```

#### Remove the line break

```{r}


```

#### Remove the two "Orange"

```{r}

```

#### Remove the unnecessary white spaces

```{r}

```

#### How long is this string? Count characters and words.

```{r}

```

#### Extract the email address

```{r}

```

#### Change the text to all lower-case

```{r}

```

#### Correct the misspelled word

```{r}

```

### More difficult

```{r}
texts <- c(
  "An apple a day keeps the doctor away, but a pineapple a day might not.",
  "She sells sea shells by the seashore, but apple pie is my favorite.",
  "Look behind you to find a treasure map that leads to an apple orchard.",
  "Look ahead of you, there is a pie waiting for you at the end of the road.",
  "We will go forward with our plan, making pineapple pie for the party.",
  "Never look back, unless you dropped your apple on the way.",
  "The future is bright with possibilities, and a slice of pie.",
  "The past is gone, but the recipe for pineapple pie remains.",
  "Pineapple is a tropical fruit, often confused with an apple.",
  "I like pineapples on my pizza, but apple pie is a classic dessert.",
  "A good pie can brighten anyone's day, especially a pineapple one.",
  "This apple pie recipe is handed down from generations.",
  "Finding a perfect apple is not easy, but making pie from it is rewarding.",
  "On a rainy day, nothing beats a warm slice of apple pie.",
  "Pineapple pies are rare, but they are a delicious twist on a classic dessert."
)
```

#### Find all sentences that mention the word "apple" directly followed by"pie"

```{r}

```

#### Find all sentences where "pie" is not directly preceded by "apple"

```{r}

```

#### Change "pineapple" to"apple" in all strings

```{r}

```
